---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# DARWIN EU StudyDiagnostics

<!-- badges: start -->
<!-- badges: end -->


- Analytics use case(s): **Characterization**
- Study type: **Phenotyping**
- Tags: **-**
- Study lead: **-**
- Study lead forums tag: **-**
- Study start date: **September 1, 2023**
- Study end date: **-**
- Protocol: **-**
- Publications: **-**
- Results explorer: **-**

Generating cohort diagnostics DARWIN EU studies.

# Instructions for installing and running the study package

Below are the instructions for installing and then running the package. For your convience, you can also find this code in [extras/CodeTorun.R](https://github.com/ohdsi-studies/PhenotypeLibraryDiagnostics/blob/master/extras/CodeToRun.R).

## How to install the study package

There are several ways in which one could install the `StudyDiagnostics` package. However, we recommend using the `renv` package:

1. See the instructions [here](https://ohdsi.github.io/Hades/rSetup.html) for configuring your R environment, including Java and RStudio.

2. In RStudio, create a new project: File -> New Project... -> New Directory -> New Project. If asked if you want to use `renv` with the project, answer ‘no’.

3. Execute the following R code:

```{r eval=FALSE}
# Install the latest version of renv:
install.packages("renv")

# Download the lock file:
download.file("https://raw.githubusercontent.com/ohdsi-studies/PhenotypeLibraryDiagnostics/master/renv.lock", "renv.lock")
  
# Build the local library. This may take a while:
renv::init()
```

## How to run the study package

1. Edit the script below to ensure that the variables contain the correct values for your environment, then execute:

```{r eval=FALSE}
library(StudyDiagnostics)

# Specify where the temporary files will be created:
options(andromedaTempFolder = "s:/andromedaTemp")

# Maximum number of cores to be used:
maxCores <- parallel::detectCores()

# Details for connecting to the server. See 
# http://ohdsi.github.io/DatabaseConnector/reference/createConnectionDetails.html for more details:
connectionDetails <- DatabaseConnector::createConnectionDetails(dbms = "...",
                                                                server = "...",
                                                                user = "...",
                                                                password = "...",
                                                                port = ...)

# For Oracle and BigQuery: define a schema that can be used to emulate temp tables. 
# You should have write access to this schema:
oracleTempSchema <- NULL

# A folder on the local file system to store results:
outputFolder <- "..."

# The database schema where the observational data in CDM is located. For SQL Server
# this should include both the database and schema, for example 'cdm.dbo'.
# You should have read access to this schema:
cdmDatabaseSchema <- "cdm"

# The database schema where the cohorts can be instantiated. For SQL Server
# this should include both the database and schema, for example 'cdm.dbo'.
# You should have write access to this schema:
cohortDatabaseSchema <- "..."

# The name of the table that will be created in the cohortDatabaseSchema:
cohortTable <- "..."

# Some meta-data about your database. The databaseId is a short (<= 20 characters)
# name for your database. The databaseName is the full name, and databaseDescription 
# provides a short (1 paragraph) description. These values will be displayed in the 
# Shiny results app for all to see.
databaseId <- "..."
databaseName <- "..."
databaseDescription <- "..." 

# This statement instatiates the cohorts, performs the diagnostics, and writes the results to
# a zip file containing CSV files. This will probaby take a long time to run:
runStudyDiagnostics(connectionDetails = connectionDetails,
                    cdmDatabaseSchema = cdmDatabaseSchema,
                    cohortDatabaseSchema = cohortDatabaseSchema,
                    cohortTable = cohortTable,
                    oracleTempSchema = oracleTempSchema,
                    outputFolder = outputFolder,
                    databaseId = databaseId,
                    databaseName = databaseName,
                    databaseDescription = databaseDescription,
                    createCohorts = TRUE,
                    runInclusionStatistics = TRUE,
                    runTimeDistributions = TRUE,
                    runBreakdownIndexEvents = TRUE,
                    runIncidenceRates = TRUE,
                    runCohortOverlap = TRUE,
                    runCohortCharacterization = TRUE,
                    runTemporalCohortCharacterization = TRUE,
                    minCellCount = 5)

# (Optionally) to view the results locally:
CohortDiagnostics::preMergeDiagnosticsFiles(file.path(outputFolder, "diagnosticsExport"))
CohortDiagnostics::launchDiagnosticsExplorer(file.path(outputFolder, "diagnosticsExport"))
```

## Sharing the results with the study coordinator

1. Upload results to the Data Transfer Zone.

# Development status

Ready to run.